---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# coursehand

**coursehand** provides methods and functions to maintain and export
the course handbooks of the Department of Statistics at University of
Warwick using Rmarkdown files. The package depends on a particular
organization of the content, so it will, most probably, not be of any
immediate use to anyone outside the Department of Statistics at
University of Warwick.

## Developed and maintained by

[Ioannis Kosmidis](http://ikosmdis.com)

## Installation

You can install the development version from
[GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ikosmidis/coursehand")
```
## Example

This is a basic example which shows you some of the methods in
**coursehand**.

```{r example}
library("coursehand")
```

### Listing handbook source files

First, we need to specify where the directory structure with the
handbook files is. For example, in my machine this is

```{r}
working_dir <- "~/Repositories/warwick-stats-handbooks"
```

Then, we can list the available Rmd files for the various courses. For
example,

```{r}
list_course_Rmd(working_dir, "datascience")
list_course_Rmd(working_dir, "mathstat")
list_course_Rmd(working_dir, "morse", full_path = FALSE)
```

We can also list the files for the common part in each handbook

```{r}
list_course_Rmd(working_dir, "common", full_path = FALSE)
```

### Rendering specific source files in HTML

If the handbook pages sit in Sitebuilder, we can update the handbook pages
one-by-one by converting the corresponding file into html format, copy
that html content into the clipboard, and then paste into the `html`
window that Sitebuilder provides. The conversion and the copying can
be done using the `Rmd_to_html()` functions. For example, the content
for
`https://warwick.ac.uk/fac/sci/statistics/currentstudents/handbooks/morse/year4mmorse-g30b/`
can be updated by editing `0210-year4mmorse-g30b.Rmd` and doing

```{r}
Rmd_to_html("0210-year4mmorse-g30b.Rmd",
            course = "morse",
            working_dir = working_dir)
```

### Compiling hanbdooks

We can compile the hanbdooks for the courses in HTML and PDF
format using [bookdown](https://bookdown.org). The output is in the
`drafts/` sub-directory under `working_directory`. For example, the
following command compiles the handbooks for the Data Science, MORSE
and MathStat courses of the Department of Statistics at University of
Warwick. 

```{r abc, warning = FALSE, eval = FALSE}
compile_book(working_dir = working_dir,
             courses = c("datascience", "morse", "mathstat"),
             include_source_names = FALSE,
             draft_version = FALSE)
```

### Retrieving module lists

We can also retrieve the module lists appearing in the handbooks. For example, the core modules in Data Science year 2 are

```{r, warning = FALSE}
module_db <- file.path(working_dir, "module_lists.csv")
get_module_list(module_db, course = "datascience", year = 2, list = "Core", bsc = "Yes")
```
